Simultaneous segmentation and registration of diffusion MR images of the brain driven by active-contours

### 2015-03-13 Publications/2015-NeuroImage/03-introduction.tex
updating references

  \begin{align}
  U\colon R \subset \mathbb{R}^n &\to M \subset \mathbb{R}^n \notag\\
  \vec{r} &\mapsto \vec{r}' =\vec{r}+u(\vec{r}),
  \label{eq:transform}
  \end{align}
%
  where $\vec{r}$ denotes a position in the reference domain $R$, $\vec{r}'$ is
  its corresponding location in $M$, and $n$ the dimensionality of images.
Finally, $\vec{u} = u(\vec{r})$ is the displacement of every point with respect
  to the reference domain.
A comprehensive survey by \cite{sotiras_deformable_2013} illustrates the wide variety
  of existing methodologies, and classifies them by their three principal building blocks:
  the matching criteria to evaluate the proximity of the solution,
  the deformation model that may implement theoretical properties of the mapping
  (i.e. linearity, elasticity, viscosity, etc.), and the optimization method.
The matching criteria can be defined as a function on the intensities of voxels of the
  two images, the alignment of spatial features derived from the corresponding objects in
  $R$ and $M$, or use both intensity and spatial informations.
In \citep{sotiras_deformable_2013} these methods are referred to as \emph{iconic}, \emph{geometric},
  and \emph{hybrid}, respectively.
When segmentation is introduced to define the matching criteria, we observe a \emph{hybrid}
  registration method that simultaneously defines a partition of the reference space to identify
  relevant objects in it.
An early integration of segmentation and registration by \cite{bertalmio_morphing_2000} proposed
  a sequential deformation of active contours for object tracking in sequential 2D images.
Shortly, \cite{yezzi_variational_2001} presented the first method including a full solution to
  the registration problem with an affine transformation supporting the coordinates mapping.
\cite{vemuri_joint_2003} proposed an atlas-based registration framework using level sets and only
  one \gls*{pde} for first time.
\cite{unal_coupled_2005} and later \cite{wang_joint_2006},
  extended the ``two \glspl*{pde}'' method of \cite{yezzi_variational_2001}
  to nonlinear registration implementing a free deformation field.
\cite{droske_mumfordshah_2009} reviewed the latter set of techniques, and proposed two different
  approaches to apply the Mumford-Shah functional \citep{mumford_optimal_1989} in simultaneous
  registration and segmentation, through the propagation of the deformation field from
  the contours to the whole image definition.
\cite{greve_accurate_2009} presented a widely used registration method called \emph{bbregister},
  included in \emph{FreeSurfer} \citep{fischl_freesurfer_2012}.
Their framework performs robust registration of brain surfaces into the intensity information
  of a target \gls*{mri}, using an affine transformation and active contours with edges.
Recently, \cite{guyader_combined_2011} proposed a simultaneous segmentation and
  registration method using level sets and a nonlinear elasticity smoother on the
  displacement vector field, which preserves topology even with very large deformations.
Finally, \cite{gorthi_active_2011} extended the existing methodologies using a multiphase
  level-set function for the registration of several active contours, in the application
  of atlas-based segmentation.
Alternatively to the historical use of active contours based methods, some Bayesian approaches
  have been proposed as well \citep{wyatt_map_2003,pohl_bayesian_2006,gass_simultaneous_2014}.

>>>>

  \begin{align}
  U\colon R \subset \mathbb{R}^n &\to M \subset \mathbb{R}^n \notag\\
  \vec{r} &\mapsto \vec{r}' =\vec{r}+u(\vec{r}),
  \label{eq:transform}
  \end{align}
%
  where $\vec{r}$ denotes a position in the reference domain $R$, $\vec{r}'$ is
  its corresponding location in $M$, and $n$ the dimensionality of images.
Finally, $\vec{u} = u(\vec{r})$ is the displacement of every point with respect
  to the reference domain.
A comprehensive survey by \cite{sotiras_deformable_2013} illustrates the wide variety
  of existing methodologies, and classifies them by their three principal building blocks:
  the matching criteria to evaluate the proximity of the solution,
  the deformation model that may implement theoretical properties of the mapping
  (i.e. linearity, elasticity, viscosity, etc.), and the optimization method.
The matching criteria can be defined as a function on the intensities of voxels of the
  two images, the alignment of spatial features derived from the corresponding objects in
  $R$ and $M$, or use both intensity and spatial informations.
In \citep{sotiras_deformable_2013} these methods are referred to as \emph{iconic}, \emph{geometric},
  and \emph{hybrid}, respectively.
When segmentation is introduced to define the matching criteria, we face a \emph{hybrid}
  registration method that simultaneously defines a partition of the reference space to identify
  relevant objects in it.
An early integration of segmentation and registration by \cite{bertalmio_morphing_2000} proposed
  a sequential deformation of active contours for object tracking in sequential 2D images.
Shortly, \cite{yezzi_variational_2003} presented the first method including a full solution to
  the registration problem with an affine transformation supporting the coordinates mapping.
\cite{vemuri_joint_2003} proposed an atlas-based registration framework using level sets and only
  one \gls*{pde} for first time.
\cite{unal_coupled_2005} and later \cite{wang_joint_2006},
  extended the ``two \glspl*{pde}'' method of \cite{yezzi_variational_2001}
  to nonlinear registration implementing a free deformation field.
\cite{droske_mumfordshah_2009} reviewed the latter set of techniques, and proposed two different
  approaches to apply the Mumford-Shah functional \citep{mumford_optimal_1989} in simultaneous
  registration and segmentation, through the propagation of the deformation field from
  the contours to the whole image definition.
\cite{greve_accurate_2009} presented a widely used registration method called \emph{bbregister},
  included in \emph{FreeSurfer} \citep{fischl_freesurfer_2012}.
Their framework performs robust registration of brain surfaces into the intensity information
  of a target \gls*{mri}, using an affine transformation and active contours with edges.
Recently, \cite{guyader_combined_2011} proposed a simultaneous segmentation and
  registration method using level sets and a nonlinear elasticity smoother on the
  displacement vector field, which preserves topology even with very large deformations.
Finally, \cite{gorthi_active_2011} extended the existing methodologies using a multiphase
  level-set function for the registration of several active contours, in the application
  of atlas-based segmentation.
Alternatively to the historical use of active contours based methods, some Bayesian approaches
  have been proposed as well \citep{wyatt_map_2003,pohl_bayesian_2006,gass_simultaneous_2014}.

### 2015-03-13 Publications/2015-NeuroImage/04-methods.tex
updating references

\subsection{Our method and contributions}
\label{sec:our_method}
\emph{Regseg} is related to \emph{bbregister}, as both methods exploit the precise
  surfaces that can be extracted with \emph{FreeSurfer}~\citep{fischl_freesurfer_2012},
  to then map this prior information into a target image.
However, \emph{bbregister} features an affine transform that is unable to compensate the
  distortions.
To avoid this problem, the active contours are dismissed in regions typically affected by
  warpings.
Additionally, \emph{bbregister} is robust in finding clear tissue boundaries.
In the case of \gls*{dmri} data, oftentimes the registration process is restricted to finding
  the pial surface, as it is the only clear boundary.

>>>>

\subsection{Our method and contributions}
\label{sec:our_method}
\emph{Regseg} is related to \emph{bbregister}, as both methods exploit the precise
  surfaces that can be extracted with \emph{FreeSurfer} \citep{fischl_freesurfer_2012},
  to then map this prior information into a target image.
However, \emph{bbregister} features an affine transform that is unable to compensate the
  distortions.
To avoid this problem, the active contours are dismissed in regions typically affected by
  warpings.
Additionally, \emph{bbregister} is robust in finding clear tissue boundaries.
In the case of \gls*{dmri} data, oftentimes the registration process is restricted to finding
  the pial surface, as it is the only clear boundary.
